---
title: "Method Comparison & Bias Estimation"
author: "https://bahar.shinyapps.io/method_compare"
date: '`r Sys.Date()`'
output: pdf_document
---

```{r dataframe, comment = '', echo=FALSE, warning = FALSE, message = FALSE}
library(mcr)
library(pander)
a <- datasetInput()
if (is.null(a)) {
return(NULL)} else {
names(a) <- c("M1", "M2")
data1 <- mcreg(a$M1, a$M2, error.ratio = input$syx, 
method.reg = input$regmodel, method.ci = input$cimethod,
method.bootstrap.ci = input$metbootci,
mref.name = input$var1, mtest.name = input$var2)
tname <- paste('X:', input$m1, '; Y:',  input$m2, '; S: Sample No.')
pander(MCResult.getData(data1), caption = tname, style = "grid")
}
```

```{r regression plot, echo=FALSE, results='markup', fig.show='asis', message = FALSE}
library(mcr)
a <- datasetInput()
if (is.null(a)) {
return(NULL)} else {
names(a) <- c("M1", "M2")
data1<- mcreg(a$M1,a$M2, error.ratio = input$syx, 
method.reg = input$regmodel, method.ci = input$cimethod,
method.bootstrap.ci = input$metbootci)
MCResult.plot(data1, ci.area=input$ciarea, 
add.legend=input$legend, identity=input$identity,
add.cor=input$addcor, x.lab=input$m1,
y.lab=input$m2, cor.method=input$cormet, 
equal.axis = TRUE, add.grid = TRUE)
}
```

```{r statistics, echo=FALSE, comment = '', warning = FALSE, message = FALSE}
library(mcr)
library(pander)
a <- datasetInput()
if (is.null(a)) {
return(NULL)} else {
names(a) <- c("M1", "M2")
data1 <- mcreg(a$M1, a$M2, error.ratio = input$syx, 
method.reg = input$regmodel, method.ci = input$cimethod,
method.bootstrap.ci = input$metbootci,
mref.name = input$var1, mtest.name = input$var2)
pander(getCoefficients(data1), caption = "Estimate (EST), standard error (SE) and upper-lower confidence interval (UCI-LCI) for intercept and slope", style = "grid")
}
```

```{r coef plot, echo=FALSE, comment = '', warning = FALSE, message = FALSE}
library(mcr)
a <- datasetInput()
if (is.null(a)) {
return(NULL)} else {
names(a) <- c("M1", "M2")
data1 <- mcreg(a$M1, a$M2, error.ratio = input$syx, 
method.reg = input$regmodel, method.ci = input$cimethod,
method.bootstrap.ci = input$metbootci,
mref.name = input$var1, mtest.name = input$var2)
compareFit(data1)
}
```

```{r BA plot, echo=FALSE, results='markup'}
library(mcr)
a <- datasetInput()
if (is.null(a)) {
return(NULL)} else {
names(a) <- c("M1", "M2")
data1 <- mcreg(a$M1, a$M2,
mref.name = input$m1, mtest.name = input$m2)
MCResult.plotDifference(data1, plot.type = input$batype, add.grid = TRUE)
}
```

```{r Bias plot, echo=FALSE, results='markup'}
library(mcr)
a <- datasetInput()
if (is.null(a)) {
return(NULL)} else {
names(a) <- c("M1", "M2")
data1<- mcreg(a$M1,a$M2, error.ratio = input$syx, 
method.reg = input$regmodel, method.ci = input$cimethod,
method.bootstrap.ci = input$metbootci)
plotBias(data1, ci.area=input$ciarea, prop=FALSE, xlab=input$m1)
}
```

```{r Per Bias plot, echo=FALSE, results='markup'}
library(mcr)
a <- datasetInput()
if (is.null(a)) {
return(NULL)} else {
names(a) <- c("M1", "M2")
data1<- mcreg(a$M1,a$M2, error.ratio = input$syx, 
method.reg = input$regmodel, method.ci = input$cimethod,
method.bootstrap.ci = input$metbootci)
plotBias(data1, ci.area=input$ciarea, prop=TRUE, xlab=input$m1)
}
```


#### Data is processed using R language^1^, shiny web application framework^2^ and mcr package^3^. shinydashboard^4^, rhandsontable^5^ and pander^6^ are used for website construction. Rmarkdown^7^ is used for converting results in to document files.

##### References and packages:

1. R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. Version: `r getRversion()` URL: https://www.R-project.org
2. shiny: Web Application Framework for R. Version `r packageDescription("shiny")$Version` URL: http://CRAN.R-project.org/package=shiny
3. mcr: Method Comparison Regression. Version: `r packageDescription("mcr")$Version` URL: http://CRAN.R-project.org/package=mcr
4. shinydashboard: Create Dashboards with 'Shiny'. Version: `r packageDescription("shinydashboard")$Version` URL: http://rstudio.github.io/shinydashboard
5. rhandsontable: Interface to the 'Handsontable.js' Library. Version: `r packageDescription("rhandsontable")$Version` URL: http://jrowen.github.io/rhandsontable
6. pander: An R Pandoc Writer. Version: `r packageDescription("pander")$Version` URL: http://rapporter.github.io/pander
7. rmarkdown: Dynamic Documents for R. Version: `r packageDescription("rmarkdown")$Version` URL: http://rmarkdown.rstudio.com
